# githapi

User-friendly access to the GitHub API for R, consistent with the tidyverse.

## Overview

GitHub is a wildly popular host for version controlled code, but also data. This package 
provides a user-friendly way to access content within GitHub through v3 of its 
[API](https://developer.github.com/v3/). The functions are also consistent with the 
[tidyverse](http://www.tidyverse.org/) approach and return tibbles where possible.

## Installation

The easiest way to install githapi is with the devtools package:

```r
library(devtools)
install_github("ChadGoymer/githapi")
```

## Usage

Most of the functions in the package are prefixed by `gh_`, except for predicate functions which are 
prefixed with `is_`.

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(githapi)
```

### Getting information about a user's repositories

The main reason for using githapi is to extract information from GitHub. For example to find all the 
repositories a user has use the function `gh_repositories()`:

```{r}
gh_repositories("ChadGoymer")
```

Information on the branches in a particular repository can then be obtained using `gh_branches()`:

```{r}
gh_branches("ChadGoymer/githapi")
```

The history of a branch can be obtained using `gh_commits()`:

```{r}
gh_commits("master", "ChadGoymer/githapi") %>% head()
```

Finally, the contents of a particular file can be returned using `gh_contents()`:

```{r}
gh_contents("DESCRIPTION", "master", "ChadGoymer/githapi") %>% cat()
```

### Authorisation

In order to access repositories in GitHub authentication is required, by setting a 
[Personal Access Token](https://help.github.com/articles/creating-a-personal-access-token-for-the-command-line/).
githapi identifies the personal token in two possible ways:

 1. On package load - if set as an environment variable named either "GITHUB_TOKEN" or "GITHUB_PAT"
 2. At any time - if set as an R option called "github.token"

Setting an R option will override the environment variable.

## Futher information

Please see the help files for each function in the package for more details.
